---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Income

The goal of income is to visualise income data of countries through plotting Lorenz-Curves.

## Installation

You can install this package with:

``` r
devtools::install_github("m-g-h/income")
```
# Example

This package is implemented via the package `drake` and should only be used inside an R-Project. After setting one up, do the following:

## 1 "Make" the drake plan:
```{r message=FALSE, warning=FALSE}
income::make_project()
```

You can take a look at the drake-plan with:
```{r fig.height=3, fig.width=7, message=TRUE, warning=TRUE}
income::show_project()
```
*(it's quite simple)*

## 2 Plot the income distributions:
```{r fig.height=3, fig.width=7}
income::plot_lorenz(ctry = "FR")
```

A list of the country id's can be shown with the function `country_list()`


